---
title: "lab1_excercises"
output: html_document
---

# Understanding Concepts 

## 1. Explain the difference between Git and Github.

Git is a revision control system that is local to your computer. Github is an online repository service that allows you to share and collaborate code with others.
  
## 2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages.

Yes it can be. We don't because they work seemlessly together and they are used together more often than not. There are other good revision control systems that you can use with github that are less cmd terminal based. 

## 3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 
 
A repository in Git is a directory or storage space where projects are held. You can create a repository locally or through Github.
1st: create a directory by using mkdir in the cmd line 
Next: git init the new directory
And you should have a new Git repository.


# Coding Exercises 

##1. 
```{r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
count <- 0
for (x in X) {
  if (is.na(x)) {
    count <- count + 1
  }
}
  print(count)
```

##2.

```{r}
age = c(25,30,45,60,12,41)
smoker = c('T','F','T','F','F','F')
weight = c(120,137,0,168,91,142)
example_data = data.frame(age,smoker,weight)
example_data[3,3] <- 150
example_data
```

##3. 
```{r, eval=FALSE}

avg <- function(x){
   return(mean(is.na(x)))
}


division <- function(x) {
  return(x/sum(x,na.rm = TRUE))
}
```
  
##4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors. 
```{r, eval=FALSE}
average <- function(x,y) {
  count <- 0
  for (i in length(x)) {
    if(is.na(x[i]) & is.na(y[i])){
      count <- count + 1
    }
  }
  return(count)
}
```
# Submission 

Once you have finished Lab 1 and after committing all of your work (don't forget to first 'git add FILENAMES'), you should  push your work to GitHub. 

Then each student (not team) should send an email titled  
`ds202 lab1` (case-sensitive) to the grader, Yunhui Qi <qyh@iastate.edu>, before by 10 pm on Thursday Sept 5. The email should contain *only* 

- Your name, student ID, github username, and GitHub repo name for Lab1, and 
- Your partner's github username, and your partner's repo name to which you made changes. 

**Note:**
Make sure that each team member has collaborated on the other member's repo. Your homework score will be the sum of each team member's score. Help out your team member in case he/she is stuck. 
